Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2024-12-28 src/docs_paper-jtb/appendix.Rmd
Editing and further material in

This section describes the simplified version of the Naomi model [@eaton2021naomi] in more detail.
The concise $i$ indexing is replaced by a more complete $x, s, a$ indexing.
There are four sections:

1. Section \@ref(naomi-process) gives the process specifications, giving the terms in each structured additive predictor, along with their distributions.
2. Section \@ref(naomi-likelihood) gives additional details about the likelihood terms.
3. Section \@ref(naomi-identifiability) gives identifiability constraints used in circumstances where incomplete data is available for the country.
4. Section \@ref(naomi-implementation) provides details of the `TMB` implementation.

@@

Table: (\#tab:process) The Naomi model can be conceptualised as having five processes. This table gives the number of latent field parameters and hyperparameters in each process, where $n$ is the number of districts in the country.

@@

ART coverage $\alpha_{x, s, a} \in [0, 1]$ was modelled on the logit scale using the structured additive predictor
\begin{equation}
\text{logit}(\alpha_{x, s, a}) = \beta^\alpha_0 + \beta_{S}^{\alpha, s = \text{M}} + \mathbf{u}^\alpha_a + \mathbf{u}_a^{\alpha, s = \text{M}} + \mathbf{u}^\alpha_x + \mathbf{u}_x^{\alpha, s = \text{M}} + \mathbf{u}_x^{\alpha, a < 15} + \boldsymbol{\mathbf{\eta}}^\alpha_{R_x, s, a} 
\end{equation}
with terms and prior distributions analogous to the HIV prevalence process model in Section \@ref(hiv-prev) above.

@@

The `TMB` C++ code for the negative log-posterior of the simplified Naomi model is available from [`https://github.com/athowes/naomi-aghq`](https://github.com/athowes/naomi-aghq).
For ease of understanding, Table \@ref(tab:tmb-lookup) provides correspondence between the mathematical notation used in Section \@ref(naomi-math) and the variable names used in the `TMB` code, for all hyperparameters and latent field parameters.
For further reference on the `TMB` software see @tmbdocumentation.

@@

@@

>>>>

This section describes the simplified version of the Naomi model [@eaton2021naomi] in more detail.
The concise $i$ indexing is replaced by a more complete $x, s, a$ indexing.
There are four sections, as follows:

1. Section \@ref(naomi-process) gives the process specifications, including the terms in each structured additive predictor, along with their distributions.
2. Section \@ref(naomi-likelihood) gives additional details about the likelihood terms.
3. Section \@ref(naomi-identifiability) gives identifiability constraints used in circumstances where incomplete data is available for the country.
4. Section \@ref(naomi-implementation) provides details of the `TMB` implementation.

@@

Table: (\#tab:process) The Naomi model can be conceptualised as having five processes. This table gives the number of latent field parameters and hyperparameters in each model component, where $n$ is the number of districts in the country.

@@

ART coverage $\alpha_{x, s, a} \in [0, 1]$ was modelled on the logit scale using the structured additive predictor
\begin{equation}
\text{logit}(\alpha_{x, s, a}) = \beta^\alpha_0 + \beta_{S}^{\alpha, s = \text{M}} + \mathbf{u}^\alpha_a + \mathbf{u}_a^{\alpha, s = \text{M}} + \mathbf{u}^\alpha_x + \mathbf{u}_x^{\alpha, s = \text{M}} + \mathbf{u}_x^{\alpha, a < 15} + \boldsymbol{\mathbf{\eta}}^\alpha_{R_x, s, a},
\end{equation}
with terms and prior distributions analogous to the HIV prevalence process model in Section \@ref(hiv-prev) above.

@@

The `TMB` C++ code for the negative log-posterior of the simplified Naomi model is available from [`https://github.com/athowes/naomi-aghq`](https://github.com/athowes/naomi-aghq).
Table \@ref(tab:tmb-lookup) maps the mathematical notation used in Section \@ref(naomi-math) to the variable names used in the `TMB` code for all hyperparameters and latent field parameters.
For further reference on the `TMB` software see @tmbdocumentation.

@@

## Posterior correlation structure

@@

## Posterior contraction
